%!TEX root = BCD.tex

%\section*{Conclusions}

\par We present the first successful ranking of a set of seven guest molecules 
with the $\beta$-cyclodextrin host using the SEEKR hybrid MD/BD/Milestoning approach.
SEEKR effectively reproduces both the magnitudes and rankings of the 
experimental off rates\cite{Fukahori2004,Fukahori2006,Nishikawa2002,Nishikawa2006,Rekharsky1998,Barros1998} and binding free energies, two quantities of interest in 
typical drug discovery campaigns\cite{Lu2010a,Schuetz2017,Copeland2006b,Copeland2016}.
%need more refs for free energy part
SEEKR also successfully differentiates the known longer residence time and 
tighter binding compounds from the weaker binding compounds. Our results are also in good agreement 
with previously conducted long timescale MD simulations for the same set of 
ligands\cite{Tang2017}. In particular SEEKR and long timescale MD simulations 
using the same forcefield (GAFF or Q4MD) exhibited similar deviations from the 
experimental values, with GAFF producing consistently faster off rates than 
experiment and Q4MD producing consistently faster on rates. In general both 
methods and both forcefields struggled to reproduce the experimental on rate 
ranking, as all ligands had very similar \kon's.
The SEEKR method requires less simulation time (3.8 ${\mu}s$ per ligand) 
than the long timescale MD approach (4.5 - 11 ${\mu}s$ per ligand). Furthermore, 
convergence analysis of the SEEKR calculations suggests that comparable results 
could be achieved with as little as 2 ${\mu}s$ per ligand. In addition, SEEKR's 
milestoning approach makes these calculations highly parallel, as the 
simulations on each milestone are completely independent from all other milestones.
%SEEKR also eliminates the need for an empirically determined definition of the 
%bound state for a system, as it is simply the innermost milestone.
We also provide an analysis of the sensitivity of the SEEKR 
calculations to various factors such as sampling, milestone spacing, and the 
construction of the milestoning model with the intention of putting forth 
``best practices'' for the use of SEEKR. SEEKR's effectiveness at ranking 
compounds for this small model system suggest that it is well suited for ranking 
compounds of more complex protein-ligand and protein-drug systems, where the 
efficiency and enhanced sampling advantages of our multiscale MD/BD/milestoning 
approach will be more apparent.
