\input{./abstract}
\input{./intro}
\input{./results-intro}
\input{./permeability}
\input{./PMFs}
\input{./diffuse}
\input{./compare}
\input{./conclusions}
\input{./methods}

\section*{Supporting Information}
Theoretical details of application of the Bayesian scheme to MD, analysis of membrane structure from MD simulations. This information is available free of charge via the Internet at http://pubs.acs.org/.

\section*{Acknowledgements}
CTL acknowledges support from the NIH Molecular Biophysics Training Program (T32-GM008326).  JC was supported by Kansas Bioscience Authority funds to the Institute of Computational Comparative Medicine (ICCM) at Kansas State University and to the Nanotechnology Innovation Center of Kansas State University (NICKS).  JCG acknowledges a CAREER award from the National Science Foundation (MCB-1452464), a Burroughs Wellcome Fund Collaborative Research Travel Grant and supercomputing resources provided by the National Institute for Computational Sciences at Oak Ridge National Lab through the Extreme Science and Engineering Discovery Environment (XSEDE), supported by NSF grant number OCI-1053575.  CNR thanks NSERC of Canada for funding through the Discovery Grant program (Application 418505-2012) and Compute Canada (RAPI: djk-615-ab) for supercomputing resources.  YW acknowledges Project 21403183 supported by National Natural Science Foundation of China.  REA acknowledges a NIH Director's New Innovator Award DP2 OD007237, the National Biomedical Computation Resource (NBCR) NIH P41 GM103426, and supercomputing resources provided by XSEDE (NSF TG-CHE060073).  REA is a co-founder of Actavalon, Inc.
